Blind Search for 21-cm Absorption Systems in New Generation Chinese Radio Telescopes

### 2017-03-15 ms_21cm.tex
foundation info

\begin{acknowledgements}
HRY acknowledges General Financial Grant No.2015M570884 and
Special Financial Grant No. 2016T90009 from the China
Postdoctoral Science Foundation.
HRY and ULP acknowledge the support of the
National Science and Engineering Research Council of Canada.
\end{acknowledgements}

>>>>

\begin{acknowledgements}
This work was supported by the National Science Foundation of China (Grants No. 11573006, 11528306), the Ministry of Science and Technology National Basic Science program (project 973) under grant No. 2012CB821804.
HRY acknowledges General Financial Grant No.2015M570884 and
Special Financial Grant No. 2016T90009 from the China
Postdoctoral Science Foundation.
HRY and ULP acknowledge the support of the
National Science and Engineering Research Council of Canada.
\end{acknowledgements}
